---
title: "LS5-Age"
author: "Gregory Jefferis"
date: "13/05/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Intro

We have manually identified key personal data for ERC grant recipients at

https://docs.google.com/spreadsheets/d/1gO661Pekx7EiaOA0AfOfGTkTpqGS_81ZP8eaMR5sWPw/edit?usp=sharing

```{r, message=FALSE}
library(googlesheets)
library(ggplot2)
library(dplyr)
```

The first time you run this, you may need to authorise access. I recommend doing this in an interactive session like so (which will open a web browser).
```{r, eval=FALSE}
googlesheets::gs_auth()
```


Read in the LS5 data from the google sheet.
```{r, message=FALSE}
gs=gs_url('https://docs.google.com/spreadsheets/d/1gO661Pekx7EiaOA0AfOfGTkTpqGS_81ZP8eaMR5sWPw/edit?usp=sharing')
LS5=gs_read(gs, ws='LS5')
```

```{r}
hist(LS5$`Applicant Age`)
```

Or showing each year:

```{r}
plot(table(LS5$`Applicant Age`))
```




```{r}
LS5 %>% 
  filter(is.finite(`Applicant Age`)) %>%
  qplot(`Year award`, `Applicant Age`, col=Sex, data = .) +
  ggbeeswarm::geom_quasirandom() +
  scale_x_continuous(breaks=function(lims) {lims=round(lims);seq.int(from=lims[1], to=lims[2], by=1)})
```

Did the consolidator eligibility rules change at some point?

## Proportion under 55

The percentage for the whole group is:
`r LS5[['Applicant Age']]<=55 / sum(is.finite(LS5[['Applicant Age']])) *100`.

What is the percentage of under 55s over time?

```{r}
LS5 %>%
  group_by(`Year award`) %>%
  filter(is.finite(`Applicant Age`)) %>%
  summarise(under55=round(100*sum(`Applicant Age`<=55)/n()),
            n=n())
```

```{r}
LS5 %>%
  filter(is.finite(`Applicant Age`)) %>%
  summarise(under55=sum(`Applicant Age`<=55)/n())
```

## Gender

Frankly the most notable thing at first glance is the very low proportion of 
female recipients:

```{r}

```

